\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}
\usepackage{enumerate}
\usepackage{bibentry}
\usepackage[square,sort,comma,numbers]{natbib}
\usepackage{natbib}
\usepackage{color} 


\name{Hongliang Li} % Your name
\address{214 Leonhard Building\\ State College, PA 16801} % Your address
\address{(814)~$\cdot$~862~$\cdot$~8126 \\ hjl5377@psu.edu}


\begin{document}

%\nobibliography{ref}

%---------------------------------------------------------------------
\begin{rSection}{Education}
{\bf Penn State University} \hfill {Expected Jun 2024} \\ 
Ph.D. in Industrial Engineering
{\bf Tianjin University} \hfill {Jan 2020}\\
M.S. in Civil Engineering
{\bf Tianjin University} \hfill {Jun 2017}\\
B.S. in Civil Engineering
\end{rSection}

%---------------------------------------------------------------------
\begin{rSection}{Research Experience}

\begin{rSubsection}{CAIS Lab, Penn State}{May 2022 - Present}{Research \& Teaching Assistant}{State college, PA}
\item Teaching assistant for IE306 and IE312 courses
\item Develop system level digital twin framework for energy efficient manufacturing system
\item Develop physics-informed machine learning models for safe robotics manipulation
\end{rSubsection}
        
\begin{rSubsection}{SJ-NTU Corp Lab, Nanyang Technological University}{Jan 2019 - Aug 2021}{Research Assistant}{Singapore}
\item Mechanism and design of cementitious composites for high performance printing using waste materials
\item Develop novel cementitious composites with phase change materials for waste cold energy harvesting in oil \& gas industry
\end{rSubsection}
        
\begin{rSubsection}{Department of Civil Engineering, Tianjin University}{Sept 2017 - Dec 2018}{Research assistant}{Tianjin, China}
\item Improve mechanical properties of crumb rubber concrete using carbon nanotubes
\end{rSubsection}
        
\end{rSection}

%-----------------------------------------------------------------
\begin{rSection}{Publications}
\vspace{-10pt}
\item {\color{blue}{Li, H.,}} Herschel, P.,Kovalenko, I., (2023). A System-Level Energy-Efficient Digital Twin Framework for Runtime Control of Batch Manufacturing Processes. In 2023 IEEE 19th International Conference on Automation Science and Engineering (CASE). {\color{blue}{Accepted}}.
\item Lu, B., {\color{blue}{Li, H.,}} Li, M., Wong, T. N., \& Qian, S. (2023). Mechanism and design of fluid catalytic cracking ash-blended cementitious composites for high performance printing. Additive Manufacturing, 61, 103286.
\item Liu, S., Lu, B., {\color{blue}{Li, H.,}} Pan, Z., Jiang, J., \& Qian, S. (2022). A comparative study on environmental performance of 3D printing and conventional casting of concrete products with industrial wastes. Chemosphere, 298, 134310.
\item Huang, Y., {\color{blue}{Li, H.,}} \& Qian, S. (2018). Self-sensing properties of engineered cementitious composites. Construction and Building Materials, 174, 253-262.
\end{rSection}

%-----------------------------------------------------------------
\begin{rSection}{Awards and Hnonors}
\vspace{-10pt}
\item {Dean's Fellowship} \hfill{Dec 2019}
\item {Dean's list, Tianjin University, Faculty of Engineering} \hfill{Jun 2017}
\item {Undergraduate Oversea Final Year Project Scholarship} \hfill{Dec 2016}
\end{rSection}

% %-----------------------------------------------------------------
% \begin{rSection}{Other activities}
% \vspace{-10pt}
% \item {High school math tutor, Jinnan Highschool} \hfill{2015-2016}
% \item {Volunteer, Boao Forum For Asia} \hfill{Apr 2014}
% \end{rSection}

% %-----------------------------------------------------------------
% \begin{rSection}{Technical Strengths}
% \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
% Computer Languages & Python, JavaScript \\
% Databases & MySQL, Microsoft SQL \\
% \end{tabular}
% \end{rSection}
\end{document}